---
title: "YHT Bull Elk Antler Size"
output: html_document
---

```{r}
library(nlme)
library(lme4)
library(sf)
library(ggplot2)
library(readr)
library(tidyr)
library(AICcmodavg)
library(dplyr)
source("C:/Users/hm114064/Documents/Git/HansMartinFunctions/NowakSurvFunctions.R")
source("C:/Users/hm114064/Documents/Git/HansMartinFunctions/theme_publication_function.R")
```
#Data required for analysis

```{r}
#Antler data downloaded from google drive
antlerdata1<-read.csv("C:/Users/hm114064/Box Sync/YaHaTindaDatabases/Bull Elk Antler Data/BullElkAntlerScores_11_30_2020.csv")
#Elk ID key -download from google drive
Elk_ID_Key <- read_csv("C:/Users/hm114064/Box Sync/YahatindaGPSData/YHT_ElkID_Alias_Lookup_Table_Updated_May_2020.csv")

#Spatial data from "Extraction of Spatial Data for YHT GPS Locations" 
elk7<-readRDS("../Extraction-of-Spatial-Data-for-YHT-Elk-GPS-Locations/spatial_survival_joined_data_2016_2020.RDS")

Age_Data1<-read_csv("C:/Users/hm114064/Box Sync/YaHaTindaDatabases/YaHaTindaAgeData/Hans_All YHT age data_5_Sept_2020.csv") 

#Migration Data
MigratoryStatus2 <- read.csv("C:/Users/hm114064/Box Sync/YaHaTindaDatabases/MigrationData/YHTMigrationClassification_2002_2020.csv", stringsAsFactors = F)
```

```{r}
#elk7<-readRDS("../Extraction-of-Spatial-Data-for-YHT-Elk-GPS-Locations/spatial_survival_joined_data_2002_2020.RDS")
#Antler score was predicted in the Antler Analysis.RMD file within Bull_Elk_Antler_Size folder
#predicted_antler_score<-read.csv("C:/Users/hm114064/Documents/Git/Bull-Elk-Antler-Size/predicted_antler_score_at_age.csv")
elk_m<- elk7 %>% as.data.frame() %>%  
  filter(Sex=="Male") %>% 
  mutate(period_length=tstop-tstart) %>% 
  mutate(season=case_when(
           month > 5 & month < 9 ~ "summer",
           month < 6 & month > 3 ~ "spring",
           month > 8 & month < 12 ~ "fall",
           month > 11 & month < 4 ~ "winter"
         ),
           wmu_banff=mwu_banff,
         age_old=case_when(
           age>3~1,
           TRUE~0
         ),
         m_dist_road.sc=scale(m_dist_road),
         m_dist_trail.sc=scale(m_dist_trail),
         log_m_dist_road=log(as.numeric(m_dist_road)+0.1)
         )
```


#Extract forage values for antler analysis
```{r}
forage_values <-  elk_m %>% 
  filter(month>5,month<9) %>% 
  group_by(elkid,Bio_year) %>% 
  dplyr::summarize(m_summer_forage=mean(m_herb,na.rm=T),
            m_summer_ndvi=mean(m_ndvi,na.rm=T)
  )
#write.csv(bull_elk_summer_forage,file="bullsummerforagevalues.csv")
#elk_m %>% group_by(Reg,status) %>% summarize(n())
```

```{r}
forage_values %>% filter(elkid=="YLM1916_YJ14")
elk_m %>% distinct(elkid,Bio_year)

elk7 %>% distinct(elkid,Bio_year)
```

```{r}


antlerdata<-antlerdata1 %>% 
  mutate(ElkEarTagID = stringr::str_trim(toupper(ElkID), side = c("both"))) %>% 
  left_join(Elk_ID_Key, by = c("ElkEarTagID" = "Alias")) %>% #Join Elk ID Key to mortality
  mutate(elkid = ifelse(is.na(Animal.IDHans),
    ElkEarTagID,
    Animal.IDHans
    ),
    elkid=replace(elkid, elkid=="UNTAGGED" | elkid=="" |elkid=="UNK"| elkid=="Untagged",NA),
    Date=as.Date(Date,format="%m/%d/%Y"),
    Bio_year = case_when(
           as.integer(format(Date,"%m"))>5 ~ as.integer(Year),
           as.integer(format(Date,"%m"))<6 ~ as.integer(Year-1))
  ) %>% 
  filter(!ElkID=="Example:") %>% 
  filter(SCI_Typical_Score!=0,
         TotalScoreRecorded=="Yes") %>% 
  dplyr::select(elkid,Year,Date,ReasonForScoring,Bio_year,SCI_Typical_Score, SCI_Gross_Score, L_MainBeam, R_MainBeam, L_Tines=Num_L_Tines._Including_Main_Beam, R_Tines=Num_R_Tines_Including_Main_Beam )



Age_Data<-Age_Data1%>% 
  mutate(ElkEarTagID = stringr::str_trim(toupper(ElkID), side = c("both"))) %>% 
  left_join(Elk_ID_Key, by = c("ElkEarTagID" = "Alias")) %>% #Join Elk ID Key to mortality
  mutate(elkid = ifelse(is.na(Animal.IDHans),
    ElkEarTagID,
    Animal.IDHans
    ),
    elkid=replace(elkid, elkid=="UNTAGGED" | elkid=="" |elkid=="UNK"| elkid=="Untagged",NA),
    Date_Captured=as.Date(Date,"%m/%d/%Y")
  ) %>% 
  filter(!is.na(elkid)) %>% 
  distinct(elkid, .keep_all = T) %>% 
  dplyr::select(elkid,Date_Captured,Age,Age_Low_Est,Age_High_Est)

 

# MigratoryStatus2<- MigratoryStatus1 %>%
#   mutate(sex = ifelse(stringr::str_detect(elkid, "^YLM"), "Male", "Female")) #%>%
#   #filter(sex=="Male")

#IF ADDING VISUAL MIGRATION OBSERVATIONS OBTAINED OUTSIDE OF THE TYPICAL MIGRATION ANALYSIS INCLUDE THIS STEP.
# BullMigratoryStatus2020 <- read.csv("C:/Users/hm114064/Box Sync/YaHaTindaDatabases/MigrationData/2020_Bull_Elk_Visual_Migration.csv", stringsAsFactors = F) %>%
#   mutate(sex = ifelse(stringr::str_detect(elkid, "^YLM"), "Male", "Female"))

# bullmig<- bind_rows(BullMigratoryStatus2020,MigratoryStatus2%>%
#   filter(sex=="Male"))

migdat <- MigratoryStatus2  %>%
  filter(sex=="Male") %>% 
  dplyr::select(elkid, year, MigratorySegmentofPop, MigrationRoute) %>% 
  mutate(elkid_year=paste(elkid,year,sep="__")) %>% 
  left_join(Elk_ID_Key, by = c("elkid" = "Alias")) %>% 
  mutate(elkid = ifelse(is.na(Animal.IDHans),
    elkid,
    Animal.IDHans
    )) %>% 
  mutate(
    tactic=replace(MigratorySegmentofPop, MigratorySegmentofPop=="unk" ,NA),
    id=elkid,
    prevyr=year-1
  )
#migdat %>% filter(elkid=="YLM1916_YJ14")

```


```{r}
# number of unique individuals in sample
length(unique(migdat$id))
```

```{r}
# Breakdown of migrants vs. residents within years (with individuals stacked across years)
with(migdat, table(year, tactic))

# Breakdown of migrants vs. residents across years (with individuals stacked across years)
with(migdat, table(tactic))

# number of observations with unknown tactic
with(migdat, length(which(is.na(tactic)==TRUE)))
```

```{r}
# individual level migration summaries
d=with(migdat, table(id,tactic)) # store table of id and tactic frequencies
length(which(d[,1]>=1 & d[,2]>=1 & d[,3]>=1 |d[,1]>=1 & d[,2]>=1|d[,2]>=1 & d[,3]>=1 |d[,1]>=1 & d[,3]>=1  )) # number of individuals that switched tactics across years
length(which(d[,1]==0 & d[,2]==0 & d[,3]==0)) # number of individuals with unknown migration status
length(which(d[,1]>=1 & d[,2]==0 & d[,3]==0)) # number of individuals that were resident across all years
length(which(d[,1]==0 & d[,2]>=1 & d[,3]==0)) # number of individuals that were eastern migratory across all years
length(which(d[,1]==0 & d[,2]==0 & d[,3]>=1)) # number of individuals that were west migratory across all years
# number of years each individual was monitored
#temp=with(migdat, data.frame(id,diff=(exit-enter)/365.25))
#d4=data.frame(temp %>% group_by(id) %>% summarise(tot=sum(diff))) # use dplyr package
#sum(d4$tot) # total number of pronghorn risk-years
#median(d4$tot) # median number of years at risk per individual
#sd(d4$tot) # standard deviation of number of years at risk per individual


```
#link antler measurements to the previous years migratory tactic
```{r}
#link antler measurements to the previous years migratory tactic
antler_prev_mig <-antlerdata %>% 
  left_join(migdat, by=c("elkid"="elkid", "Bio_year"="year")) %>% 
  filter(!is.na(MigratorySegmentofPop)) 
nrow(antler_prev_mig)
nrow(antlerdata)

#If previous years migratory tactic is not know, use the following years migratory tactic.
antler_mig <- antlerdata %>%
  anti_join(antler_prev_mig, by=c("elkid"="elkid", "Date"="Date")) %>%  #antijoin with antler measurements previously joined with mig status
  left_join(migdat , by=c("elkid"="elkid","Bio_year"="prevyr"))
nrow(antlerdata)-(nrow(antler_prev_mig)+nrow(antler_mig))
```

```{r}
ant_mig_age_data<-bind_rows(antler_prev_mig,antler_mig) %>% 
  left_join(Age_Data,by=c("elkid"="elkid"))
#Age_Low_Est,Age_High_Est
ant_mig_age_data<-animal_age(ant_mig_age_data,
                             date = Date, 
                             date_captured = Date_Captured,
                             age_at_cap =Age_Low_Est) %>% 
  mutate(agelow=age)
ant_mig_age_data<-animal_age(ant_mig_age_data,date = Date,
                             date_captured = Date_Captured,
                             age_at_cap =Age_High_Est) %>% 
  mutate(agehigh=age)
#Add NDVI and Herbaceous forage data the elk used in summer (see extraction of spatial survival analysis)
ant_mig_age_forage_data<-ant_mig_age_data %>% 
  left_join(forage_values, by=c("elkid"="elkid", "Bio_year"="Bio_year"))

ant_mig_age_forage_all_data<-ant_mig_age_forage_data %>% 
  mutate(
    age.fact=factor(age, levels=c("1","2","3","4","5","6")),
    age.2=age*age,
    m_summer_forage.2=m_summer_forage^2,
    Bio_year.fact=factor(Bio_year,levels=c("2017","2018","2019","2020")),
    elkid.fact=as.factor(elkid))

```

GLM analysis of bull elk antler growth by age and migratory tactic
```{r}
ggplot(data=ant_mig_age_data, aes(x = age, fill=tactic))+
  geom_histogram()
head(ant_mig_age_data)

```
```{r}

ant_mig_age_forage_all_data %>% 
  mutate(max_tines=pmax(L_Tines,R_Tines,na.rm=T)) %>% 
  filter(!is.na(max_tines),!is.na(age)) %>% 
  group_by(age,max_tines) %>% 
  summarize(numind=n()) %>% 
  group_by(age) %>% 
  mutate(prop=numind/sum(numind)) %>% 
  ungroup() %>% 
  dplyr::select(age,max_tines,prop) %>% 
  spread(key=max_tines,value=prop)# %>% write.csv("./Results/Pts_age.csv")

```
#Remove na values for age, tactic, and forage
```{r}
#number of antler scores missing age data
ant_mig_age_forage_all_data %>% filter(is.na(age))# %>% nrow()
```


```{r}
Age_Data %>% filter(elkid=="YLM1828_YO15")

```
```{r}
#number of antler scores with a migratory tactic assigned- if na - i.e. for animals captured in one year the next year's migratory tactic is assigned becuase one 2 individuals switched tactics between years.
ant_mig_age_forage_all_data %>% filter(!is.na(tactic)) %>% nrow()
#Check and make sure all antler measurements missing migratory tactic are from captures or uncollared animals.
ant_mig_age_forage_all_data %>% filter(is.na(tactic))
```
```{r}
#number of antler scores missing forage data
ant_mig_age_forage_all_data %>% filter(is.na(m_summer_forage)) %>% nrow()

#number of antler scores with forage data
ant_mig_age_forage_all_data %>% filter(!is.na(m_summer_forage)) %>% nrow()
```
```{r}
#number of antler scores from captures vs harvest/mortality
ant_mig_age_forage_all_data %>% group_by(ReasonForScoring) %>% summarise(n())
```


#Random effect models for different metrics of age
##Model selection for age as a factor influencing antler size

```{r}
cand.models<-NULL
cand.models<-list()

cand.models[[1]]<-lme(SCI_Gross_Score~age,
                       random=~1|elkid,
                      data = ant_mig_age_forage_all_data,
                      na.action=na.exclude)

cand.models[[2]]<-lme(SCI_Gross_Score~age+age.2,
                       random=~1|elkid,
                       data = ant_mig_age_forage_all_data,
                      na.action=na.exclude)

cand.models[[3]]<-lme(SCI_Gross_Score~age.fact,
                        random=~1|elkid,
                      data = ant_mig_age_forage_all_data,
                      na.action=na.exclude)



Forage_Modnames <- paste("mod", 1:length(cand.models), sep = " ")
#bictab(cand.set = cand.models, modnames = Forage_Modnames, sort = TRUE,method=ML)
print(bictab(cand.set = cand.models, modnames = Forage_Modnames, sort = TRUE),
     digits = 4, LL = TRUE)
```
#Random effect models for different metrics of age.fact, bio_year, and migratory tactic
##Model selection for age as a factor influencing antler size
```{r}
cand.models<-NULL
cand.models<-list()
cand.models[[1]]<-lme(SCI_Gross_Score~age.fact+tactic, #tactic is not significant
                        random=~1|elkid,
                      data = ant_mig_age_forage_all_data,
                      na.action=na.exclude)

cand.models[[2]]<-lme(SCI_Gross_Score~age.fact+Bio_year.fact, #biological year is only significant for 2017 and 2018
                        random=~1|elkid,
                      data = ant_mig_age_forage_all_data,
                      na.action=na.exclude)

cand.models[[3]]<-lme(SCI_Gross_Score~age.fact+Bio_year.fact+tactic,#tactic is not significant
                        random=~1|elkid,
                      data =ant_mig_age_forage_all_data,
                      na.action=na.exclude)

 
Forage_Modnames <- paste("mod", 1:length(cand.models), sep = " ")
#bictab(cand.set = cand.models, modnames = Forage_Modnames, sort = TRUE,method=ML)
##round to 4 digits after decimal point and give log-likelihood
print(bictab(cand.set = cand.models, modnames = Forage_Modnames, sort = TRUE),
     digits = 4, LL = TRUE)

```
#top model but tactic is still not significant. Once tactic is included however, 2018 bioyear becomes significant
```{r}
summary(cand.models[[3]])
```

#Random effect models for different metrics of age.fact, bio_year, and summer forage biomass and ndvi
##Model selection for age as a factor influencing antler size
```{r}
cand.models<-list()

cand.models[[1]]<-lme(SCI_Gross_Score ~ age.fact,
                       random=~1|elkid,
                      data = ant_mig_age_forage_all_data %>% filter(!is.na(m_summer_forage)),
                      na.action=na.exclude)

cand.models[[2]]<-lme(SCI_Gross_Score ~ age.fact + m_summer_forage,
                       random=~1|elkid,
                      data = ant_mig_age_forage_all_data %>% filter(!is.na(m_summer_forage)),
                      na.action=na.exclude)

cand.models[[3]]<-lme(SCI_Gross_Score ~ age.fact+ m_summer_ndvi,
                       random=~1|elkid,
                       data = ant_mig_age_forage_all_data%>% filter(!is.na(m_summer_forage)),
                      na.action=na.exclude)

cand.models[[4]]<-lme(SCI_Gross_Score~age.fact + m_summer_forage + m_summer_forage.2,
                        random=~1|elkid,
                      data = ant_mig_age_forage_all_data%>% filter(!is.na(m_summer_forage)),
                      na.action=na.exclude)


Forage_Modnames <- paste("mod", 1:length(cand.models), sep = " ")
#bictab(cand.set = cand.models, modnames = Forage_Modnames, sort = TRUE,method=ML)
##round to 4 digits after decimal point and give log-likelihood
print(bictab(cand.set = cand.models, modnames = Forage_Modnames, sort = TRUE),
     digits = 4, LL = TRUE)
```
```{r}
summary(cand.models[[2]])

```

#Top model with random effect
########################
#########################
```{r}
#rep_ant_data<-
  # ant_mig_age_data %>% 
  # group_by(elkid) %>% 
  # filter(n()>1) %>% 
  # dplyr::select(elkid,age,SCI_Gross_Score) %>% 
  # spread(age,SCI_Gross_Score)

library(nlme)
library(merTools)
ggplot(ant_mig_age_data %>% 
  group_by(elkid) %>% 
  filter(n()>1),aes(x=age,y=SCI_Gross_Score, col=elkid))+
  geom_line()

rndeff<-lme(fixed=SCI_Gross_Score~age.fact,
          random=~1+age|elkid,
          data=ant_mig_age_forage_all_data,
          na.action=na.exclude)
newdat<-tibble::tibble(age.fact=factor(c(2,3,4,5,6),levels=c("2","3","4","5","6")))
cand.models[[5]]


rndeff<-lme(fixed=SCI_Gross_Score~ age.fact,
          #random=~1|elkid,
          data=ant_mig_age_forage_data,
          na.action=na.exclude)

newdat$pred_score<-predictInterval(rnd_eff_model,newdata = newdat)[,1]

summary(rndeff)

ant_mig_age_forage_data$pred_score<-predict(rndeff)

ggplot(ant_mig_age_forage_data ,aes(x=age.fact,y=pred_score))+
  geom_line()
```



```{r}
pred_data<-tibble::tibble(elkid=rep(unique(ant_mig_age_data$elkid),each=7), age=rep(1:7, times=length(unique(ant_mig_age_data$elkid))), age.2=age^2) %>% 
  mutate(age.fact=factor(age,levels=c("1","2","3","4","5","6","7")))

 ant_mig_age_forage_all_data<-ant_mig_age_forage_all_data%>% 
  mutate(
    age.fact=factor(age, levels=c("1","2","3","4","5","6","7")),
    age.2=age*age,
    Bio_year.fact=factor(Bio_year,levels=c("2017","2018","2019","2020")),
    elkid.fact=as.factor(elkid))
#pred_data$pred_score<-predict(rndeff)
# rnd_eff_model<-lmer(SCI_Gross_Score ~ age+age.2 + m_summer_forage + (1|elkid), data=ant_mig_age_forage_all_data)

# <-lme(SCI_Gross_Score~age.fact+tactic +m_summer_forage+m_summer_forage*m_summer_forage,
#                         random=~1|elkid,
#                       data = ant_mig_age_forage_all_data,
#                       na.action=na.exclude)
 
rnd_eff_model<-lmer(SCI_Gross_Score ~ age+age.2 +  (1|elkid), data=ant_mig_age_forage_all_data)

pred_data$pred_score<-predictInterval(rnd_eff_model,newdata = pred_data)[,1]

pred_data1<-pred_data %>% 
  left_join(Age_Data,by=c("elkid"="elkid")) %>%
  mutate(Bio_Year=as.integer(format(Date_Captured,"%Y"))-as.integer(Age)+age-1) %>%
  left_join(ant_mig_age_data %>%
              dplyr::select(elkid,age,SCI_Gross_Score), 
            by=c("elkid"="elkid", "age"="age")
            )


pred_data1 %>% filter(elkid=="YLM1906")
write.csv(pred_data1, "predicted_antler_score_at_age.csv")
```

```{r}

pred_data_age<-tibble::tibble(elkid=NA,age=seq(from=1, to=6,by = 0.1), age.2=age^2) %>% 
  mutate(#age.fact=factor(age,levels=c("1","2","3","4","5","6")),
         pred_score=56.454+age*64.594+age.2*-3.852)



pred_data_age$pred_score<-predictInterval(rnd_eff_model,newdata = pred_data_age)[,1]

ggplot(pred_data_age,aes(x= age,y=pred_score))+
  geom_line()+
  geom_abline()
  
ggplot(pred_data ,aes(x=age,y=pred_score, col=elkid))+
  geom_point()
```
#ONLY AGE AS PREDICTOR
```{r}
Age_Age2_model<-glm(SCI_Gross_Score~age+age.2,
                        
                      data = ant_mig_age_forage_all_data,
                      na.action=na.exclude)

summary(Age_Age2_model)
pred.age<-rep(seq(0,6,0.01),times=4)
pred.age.2<-(pred.age^2)


pred.bio_year<-factor(rep(c("2017","2018","2019","2020"),each=length(pred.age)/4,levels=c("2017","2018","2019","2020")))

#pred_line<-predict(cand.models[[2]],list(age=seq(0,10,0.01)) ,type="response", se.fit=T)
#linear_predictions<-tibble::tibble(pred.age=seq(0,10,0.01), fit=pred_line$fit, LCI=pred_line$fit-1.96*pred_line$se.fit,UCI=pred_line$fit+1.96*pred_line$se.fit)

pred <- predict(Age_Age2_model,list(age=pred.age, age.2=pred.age.2,Bio_year.fact=pred.bio_year ) ,type="response", se.fit=T)

predictions<-tibble::tibble(pred.age=pred.age,pred.age.2=pred.age.2,Bio_year.fact=pred.bio_year, fit=pred$fit, LCI=pred$fit-1.96*pred$se.fit,UCI=pred$fit+1.96*pred$se.fit)
```
```{r}
library(nlme)
library(lme4)
topmod<-lme(SCI_Gross_Score~age+age.2+Bio_year.fact, random=~1|elkid,data = ant_mig_age_data,na.action=na.omit)
coef(topmod)
summary(topmod)
```

#Predict age + age.2 antler relationship
```{r}

summary(Age_Age2_model)
pred.age<-rep(seq(0,6,0.01))
pred.age.2<-(pred.age^2)

#pred.bio_year<-factor(rep(c("2017","2018","2019","2020"),each=length(pred.age)/4,levels=c("2017","2018","2019","2020")))

pred_line<-predict(Age_Age2_model,list(age=seq(0,10,0.01)) ,type="response", se.fit=T)
# linear_predictions<-tibble::tibble(pred.age=seq(0,10,0.01), fit=pred_line$fit, LCI=pred_line$fit-1.96*pred_line$se.fit,UCI=pred_line$fit+1.96*pred_line$se.fit)

pred <- predict(Age_Age2_model,list(age=pred.age, age.2=pred.age.2,Bio_year.fact=pred.bio_year ) ,type="response", se.fit=T)

predictions<-tibble::tibble(pred.age=pred.age,pred.age.2=pred.age.2, fit=pred$fit, LCI=pred$fit-1.96*pred$se.fit,UCI=pred$fit+1.96*pred$se.fit)
```

antler growth vs age 
```{r}
colorspal<-wesanderson::wes_palette("BottleRocket2", 4, type = c("discrete"))
#load Windows font Times New Roman
windowsFonts(Times = windowsFont("Times New Roman"))

f1<-ggplot( data=predictions,aes(x=pred.age,y=fit))+
  geom_line(size=0.75)+
  #geom_line(aes(pred.age, y=pred_line),color="black", size=1)+
  geom_ribbon(aes(ymin=LCI, ymax=UCI), alpha=0.15)+
  geom_point(data=ant_mig_age_forage_all_data, aes(x=age,y=SCI_Gross_Score, colour=Bio_year.fact))+
  #scale_colour_manual(values=c("#0072B2", "#D55E00", "#CC79A7"),labels=c("2017","2018","2019"))+
  #scale_fill_manual(values=c("#0072B2", "#D55E00", "#CC79A7"), guide=F)+
  labs(y="SCI Gross Score", x = "Age", colour= "Year")+theme_classic() +
  scale_y_continuous(limits=c(70,350))+
  scale_x_continuous(breaks=c(1,2,3,4,5,6),limits=c(1,6))+
  theme(axis.text.y = element_text(size=14, family="Times"),axis.text.x = element_text(size=14, family="Times"),axis.title.x=element_text(size=14, family="Times"),
                axis.title.y=element_text(size=14, family="Times"),legend.title=element_text(size=14, family="Times"),
                legend.text=element_text(size=14, family="Times"),legend.position=c(0.75,0.25))#+ #scale_fill_manual(name="Year",breaks=c("2017","2018","2019","2020"),values=c("2017"=colorspal[1],"2018"=colorspal[2],"2019"=colorspal[3],"2020"=colorspal[4], "linear"="Black"))  + 
  #scale_color_manual(name="Year",breaks=c("2017","2018","2019","2020"),values=c("2017"=colorspal[1],"2018"=colorspal[2],"2019"=colorspal[3],"2020"=colorspal[4]))
  f1
tiff("AntlerSize_Age+Age2.tif", units="in", width=6, height=5, res=600, compression = "lzw")
f1
dev.off() 
 #linear vs. non-linear
```
#Predict age  antler relationship
```{r}
Age_model<-glm(SCI_Gross_Score~age,
                        
                      data = ant_mig_age_forage_all_data,
                      na.action=na.exclude)
summary(Age_Age2_model)
pred.age<-rep(seq(0,6,0.01))
pred.age.2<-(pred.age^2)

#pred.bio_year<-factor(rep(c("2017","2018","2019","2020"),each=length(pred.age)/4,levels=c("2017","2018","2019","2020")))

pred_line<-predict(Age_model,list(age=seq(0,6,0.01)) ,type="response", se.fit=T)
linear_predictions<-tibble::tibble(pred.age=seq(0,6,0.01), fit=pred_line$fit, LCI=pred_line$fit-1.96*pred_line$se.fit,UCI=pred_line$fit+1.96*pred_line$se.fit)

# pred <- predict(Age_model,list(age=pred.age, age.2=pred.age.2,Bio_year.fact=pred.bio_year ) ,type="response", se.fit=T)

predictions_age<-tibble::tibble(pred.age=pred.age,pred.age.2=pred.age.2, fit=pred$fit, LCI=pred$fit-1.96*pred$se.fit,UCI=pred$fit+1.96*pred$se.fit)
```
antler growth vs age 
```{r}
#load Windows font Times New Roman
windowsFonts(Times = windowsFont("Times New Roman"))

f2<-ggplot( data=linear_predictions,aes(x=pred.age,y=fit))+
  geom_line(size=1,color="black")+
  geom_ribbon(aes(ymin=LCI, ymax=UCI, color=NULL), alpha=0.15)+
  geom_point(data=ant_mig_age_data, aes(x=age,y=SCI_Gross_Score, colour=tactic))+
  #scale_colour_manual(values=c("#0072B2", "#D55E00", "#CC79A7"),labels=c("2017","2018","2019"))+
  #scale_fill_manual(values=c("#0072B2", "#D55E00", "#CC79A7"), guide=F)+
  labs(y="SCI Gross Score", x = "Age", colour= "tactic")+theme_classic() +scale_y_continuous(limits=c(70,500))+scale_x_continuous(breaks=c(2,3,4,5,6,7,8,9),limits=c(2,9))+
  theme(axis.text.y = element_text(size=14, family="Times"),axis.text.x = element_text(size=14, family="Times"),axis.title.x=element_text(size=14, family="Times"),
                axis.title.y=element_text(size=14, family="Times"),legend.title=element_text(size=14, family="Times"),
                legend.text=element_text(size=14, family="Times"),legend.position=c(0.25,0.15))

f2
tiff("AntlerSizeLinear.tif", units="in", width=6, height=5, res=600, compression = "lzw")
f2
dev.off() 
 
```


#FecalN

```{r}
#fecal<-read.csv("C:/Users/hm114064/Box Sync/YaHaTindaDatabases/FecalNData/2019 Summer Fecal NOTDNA.csv") %>% select(fN=TN, tactic=Location,Sex=Sex)# %>% filter(Sex=="M")

fecal<-read.csv("C:/Users/hm114064/Box Sync/YaHaTindaDatabases/FecalNData/SummerFecalN.csv") %>% dplyr::select(fN=TN..w.w.., tactic=Location_corrected,Sex=SEX_HighConfidence.and.DNA, Year) 

fecal %>% group_by(tactic, Sex) %>% summarize(mean=mean(fN), sd=sd(fN),N=n())

fn_male_tactic<-aov(fN~tactic*Sex, data=fecal)

summary(fn_male_tactic)

```

```{r}
p<-ggplot(fecal,aes(tactic,fN, colour=Sex))+
  geom_boxplot()+
  theme_classic()+
  theme(
    axis.text.y = element_text(size=14, family="Times"),
    axis.text.x = element_text(size=14, family="Times"),
    axis.title.x=element_blank(),
    axis.title.y=element_text(size=14, family="Times"),legend.title=element_text(size=14, family="Times"),
    legend.text=element_text(size=14, family="Times"),legend.position=c(0.15,0.15)) #+
  #xlab=element_blank()
#+
  # scale_fill_manual(name="Migratory tactic",
  #                   breaks=c("Resident","East","West"),
  #                   values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))  +
  # scale_color_manual(name="Migratory tactic",
  #                    breaks=c("Resident","East","West"),
  #                    values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))
#tiff("Fecal_N_dna.tif", units="in", width=6, height=5, res=600, compression = "lzw")
p
#dev.off()  
```

```{r}
p<-ggplot(fecal,aes(tactic,fN, fill=Sex))+
  geom_boxplot(color="black")+
  ylab("Total Fecal Nitrogen (w/w%")+
  theme_classic()+
  theme(
    axis.text.y = element_text(size=14, family="Times"),
    axis.text.x = element_text(size=14, family="Times"),
    axis.title.x=element_blank(),
    axis.title.y=element_text(size=14, family="Times"),legend.title=element_text(size=14, family="Times"),
    legend.text=element_text(size=14, family="Times"),legend.position=c(0.15,0.15)) #+
  #xlab=element_blank()
#+
  # scale_fill_manual(name="Migratory tactic",
  #                   breaks=c("Resident","East","West"),
  #                   values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))  +
  # scale_color_manual(name="Migratory tactic",
  #                    breaks=c("Resident","East","West"),
  #                    values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))
p
tiff("./Results/Male_Female_Fecal_N.tif", units="in", width=6, height=5, res=600, compression = "lzw")
p
dev.off()  
```

```{r}
p<-ggplot(fecal %>% filter(Year=="2017"),aes(tactic,fN))+
  geom_boxplot(color="black")+
  theme_classic()+
  ylab("Total Fecal Nitrogen (w/w%")+
  theme(
    axis.text.y = element_text(size=14, family="Times"),
    axis.text.x = element_text(size=14, family="Times"),
    axis.title.x=element_blank(),
    axis.title.y=element_text(size=14, family="Times"),legend.title=element_text(size=14, family="Times"),
    legend.text=element_text(size=14, family="Times"),legend.position=c(0.15,0.15)) #+
  #xlab=element_blank()
#+
  # scale_fill_manual(name="Migratory tactic",
  #                   breaks=c("Resident","East","West"),
  #                   values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))  +
  # scale_color_manual(name="Migratory tactic",
  #                    breaks=c("Resident","East","West"),
  #                    values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))
p
tiff("Female_Fecal_N.tif", units="in", width=6, height=5, res=600, compression = "lzw")
p
dev.off()  
```

```{r}
Mig<-bind_rows(MigratoryStatus2, BullMigratoryStatus2020) %>% 
  filter(MigratorySegmentofPop!="unk", year>2017) %>%  
  mutate(sex = ifelse(stringr::str_detect(elkid, "^YLM"), "Male", "Female")) %>% 
  mutate(
    tactic=replace(MigratorySegmentofPop, MigratorySegmentofPop=="unk" ,NA)) %>%
  group_by(sex,tactic)  %>% 
 summarise(Percentage=n()) %>% 
 group_by(sex) %>% 
 mutate(Percentage=Percentage/sum(Percentage)*100)

write.csv(Mig, "YHT_proportion_migratory_tactic_2018-2019.csv")


p<-ggplot(Mig %>% group_by(sex),aes(x=tactic,y=Percentage, colour=sex, fill=sex))+
  geom_bar(position="dodge", stat="identity")+
  ylab("Percentage of Population")+
  theme_classic()+
  theme(
    axis.text.y = element_text(size=18, family="Times"),
    axis.text.x = element_text(size=18, family="Times"),
    axis.title.x=element_blank(),
    axis.title.y=element_text(size=18, family="Times"),
    legend.title=element_text(size=18, family="Times"),
    legend.text=element_text(size=18, family="Times"))#,legend.position=c(0.15,0.15)) #+
  #xlab=element_blank()
tiff("ProportionofMigrants.tif", units="in", width=6, height=5, res=600, compression = "lzw")
p
dev.off()  
```






  geom_histogram(stat=,color="black")+
  theme_classic()+
  ylab("Total Fecal Nitrogen (w/w%")+
  theme(
    axis.text.y = element_text(size=14, family="Times"),
    axis.text.x = element_text(size=14, family="Times"),
    axis.title.x=element_blank(),
    axis.title.y=element_text(size=14, family="Times"),legend.title=element_text(size=14, family="Times"),
    legend.text=element_text(size=14, family="Times"),legend.position=c(0.15,0.15)) #+
  #xlab=element_blank()
#+
  # scale_fill_manual(name="Migratory tactic",
  #                   breaks=c("Resident","East","West"),
  #                   values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))  +
  # scale_color_manual(name="Migratory tactic",
  #                    breaks=c("Resident","East","West"),
  #                    values=c("Resident"="#E69F00","East"="#999999","West"="#56B4E9"))
tiff("Female_Fecal_N.tif", units="in", width=6, height=5, res=600, compression = "lzw")
p
dev.off()  
```
